Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-12-12 paper.tex
less -> fewer ?

Ciphers are described as operating on a ``state'', initialized to be
the plaintext and read off at the end as the ciphertext. This state is
updated by a ``round'' function that is repeated a given number of
times (of the order of ten iterations). The exact number of iterations
is a trade-off between latency (less iterations means faster
computation) and security (more iterations makes for more costly
cryptanalysis effort). The round function itself is built
compositionally from 3 components: a key mixing layer (making the
encryption process reversible), a confusion layer (smoothing local
correlations among the inputs) and a diffusion layer (spreading
correlations across the whole output block).

>>>>

Ciphers are described as operating on a ``state'', initialized to be
the plaintext and read off at the end as the ciphertext. This state is
updated by a ``round'' function that is repeated a given number of
times (of the order of ten iterations). The exact number of iterations
is a trade-off between latency (fewer iterations means faster
computation) and security (more iterations makes for more costly
cryptanalysis effort). The round function itself is built
compositionally from 3 components: a key mixing layer (making the
encryption process reversible), a confusion layer (smoothing local
correlations among the inputs) and a diffusion layer (spreading
correlations across the whole output block).
